Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2018-10-31 SupportingInformation.Rmd
editted all

  m<-matrix(NA,1,17)
  colnames(m)<-c("num.pairs","num.non-indep","num.non-N",
                 "Avg.best.AICw","Avg.N.AICw","num.good.fit",
                 "0.025-CI.LT","0.975-CI.LT","0.025-CI.UT","0.975-CI.UT",
                 "num.LT-UT>0",
                 "0.025-CI.Pl","0.975-CI-Pl","0.025-CI.Pu","0.975-CI.Pu","0.025-CI.Pl-Pu","0.975-CI.Pl-Pu")
  m<-as.data.frame(m)

@@

  d<-dim(r$gfc_numBS)[1]
  m$num.pairs<-(d^2)-d 
  m$`num.non-indep`<- (d^2)-d-2*(r$num_indep_loc_pair+r$num_neg_cor_loc_pair)
  m$`num.non-N`<-sum(r$info_ord_copcode[,,1]!=1,na.rm = T)
  r$info_ord_AICw[r$info_ord_AICw==Inf] <- NaN
  m$Avg.best.AICw<-round(mean(r$info_ord_AICw[,,1],na.rm = T),3)
  normal_AICw[normal_AICw==Inf]<-NaN
  m$Avg.N.AICw<-round(mean(normal_AICw,na.rm=T),3)
  temp<-which((r$gfc_p_CvM>0.01) & (r$gfc_p_KS>0.01),arr.ind=T)
  m$num.good.fit<-dim(temp)[1]
  t<-r$LTdep_AICw[is.finite(r$LTdep_AICw)]
  CI_LT<-unname(quantile(t,probs=c(0.025,0.975),na.rm = T))
  m$`0.025-CI.LT`<-round(CI_LT[1],3)
  m$`0.975-CI.LT`<-round(CI_LT[2],3)
  t<-r$UTdep_AICw[is.finite(r$UTdep_AICw)]
  CI_UT<-unname(quantile(t,probs=c(0.025,0.975),na.rm = T))
  m$`0.025-CI.UT`<-round(CI_UT[1],3)
  m$`0.975-CI.UT`<-round(CI_UT[2],3)
  m$`num.LT-UT>0`<-sum(r$LTdep_AICw-r$UTdep_AICw>0,na.rm=T)
  m$`0.025-CI.Pl`<-round(rs$numericdf[5,3],3)
  m$`0.975-CI-Pl`<-round(rs$numericdf[5,4],3)
  m$`0.025-CI.Pu`<-round(rs$numericdf[6,3],3)
  m$`0.975-CI.Pu`<-round(rs$numericdf[6,4],3)
  m$`0.025-CI.Pl-Pu`<-round(rs$numericdf[10,3],3)
  m$`0.975-CI.Pl-Pu`<-list(round(rs$numericdf[10,4],3))
  #m$CI_Pl<-list(c(round(rs$numericdf[5,3],3),round(rs$numericdf[5,4],3)))
  #m$CI_Pu<-list(c(round(rs$numericdf[6,3],3),round(rs$numericdf[6,4],3)))
  #m$`CI_Pl-Pu`<-list(c(round(rs$numericdf[10,3],3),round(rs$numericdf[10,4],3)))

>>>>

  m<-matrix(NA,1,17)
  colnames(m)<-c("num.pairs","num.non-indep","num.non-N",
                 "Avg.best.AICw","Avg.N.AICw","num.good.fit",
                 "0.025-CI.LT","0.975-CI.LT","0.025-CI.UT","0.975-CI.UT",
                 "percent.LT-UT>0",
                 "0.025-CI.Pl","0.975-CI-Pl","0.025-CI.Pu","0.975-CI.Pu","0.025-CI.Pl-Pu","0.975-CI.Pl-Pu")
  m<-as.data.frame(m)

@@

  d<-dim(r$gfc_numBS)[1]
  m$num.pairs<-(d^2)-d 
  m$`num.non-indep`<- (d^2)-d-2*(r$num_indep_loc_pair+r$num_neg_cor_loc_pair)
  m$`num.non-N`<-sum(r$info_ord_copcode[,,1]!=1,na.rm = T)
  r$info_ord_AICw[r$info_ord_AICw==Inf] <- NaN
  m$Avg.best.AICw<-round(mean(r$info_ord_AICw[,,1],na.rm = T),3)
  normal_AICw[normal_AICw==Inf]<-NaN
  m$Avg.N.AICw<-round(mean(normal_AICw,na.rm=T),3)
  temp<-which((r$gfc_p_CvM>0.01) & (r$gfc_p_KS>0.01),arr.ind=T)
  m$num.good.fit<-dim(temp)[1]
  t<-r$LTdep_AICw[is.finite(r$LTdep_AICw)]
  CI_LT<-unname(quantile(t,probs=c(0.025,0.975),na.rm = T))
  m$`0.025-CI.LT`<-round(CI_LT[1],3)
  m$`0.975-CI.LT`<-round(CI_LT[2],3)
  t<-r$UTdep_AICw[is.finite(r$UTdep_AICw)]
  CI_UT<-unname(quantile(t,probs=c(0.025,0.975),na.rm = T))
  m$`0.025-CI.UT`<-round(CI_UT[1],3)
  m$`0.975-CI.UT`<-round(CI_UT[2],3)
  m$`percent.LT-UT>0`<-round((sum(r$LTdep_AICw-r$UTdep_AICw>0,na.rm=T)/((d^2)-d-2*(r$num_indep_loc_pair+r$num_neg_cor_loc_pair)))*100,2)
  m$`0.025-CI.Pl`<-round(rs$numericdf[5,3],3)
  m$`0.975-CI-Pl`<-round(rs$numericdf[5,4],3)
  m$`0.025-CI.Pu`<-round(rs$numericdf[6,3],3)
  m$`0.975-CI.Pu`<-round(rs$numericdf[6,4],3)
  m$`0.025-CI.Pl-Pu`<-round(rs$numericdf[10,3],3)
  m$`0.975-CI.Pl-Pu`<-list(round(rs$numericdf[10,4],3))
  #m$CI_Pl<-list(c(round(rs$numericdf[5,3],3),round(rs$numericdf[5,4],3)))
  #m$CI_Pu<-list(c(round(rs$numericdf[6,3],3),round(rs$numericdf[6,4],3)))
  #m$`CI_Pl-Pu`<-list(c(round(rs$numericdf[10,3],3),round(rs$numericdf[10,4],3)))
